Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2021-11-01 sports_analytics.Rmd
Quang's author info

---
title: "Big Ideas in Sports Analytics and Statistical Tools for their Investigation"
authors:
  - name: Benjamin S. Baumer
    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
    department: Statistical & Data Sciences
    affiliation: Smith College
    location: Northampton, MA 01063
    email: bbaumer@smith.edu
    ORCID: 0000-0002-3279-0516
  - name: Gregory J. Matthews
    department: Mathematics and Statistics
    affiliation: Loyola University Chicago
    location: Chicago, IL 60660
    email: gmatthews1@luc.edu
    ORCID: 0000-0002-8413-5097
abstract: |
  Sports analytics---broadly defined as the pursuit of improvement in athletic performance through the analysis of data---has expanded its footprint both in the professional sports industry and in academia over the past 30 years. We connect four(?) big ideas that are common across multiple sports, and explore both the shared similarities and individual idiosyncracies of analytical approaches in each sport. While our focus is on the concepts underlying each type of analysis, any implementation necessarily involves both statistical methodologies and sources of data. Where appropriate, we outline how data, models, and knowledge of the sport combine to generate actionable insights. This paper should serve as a useful overview for anyone becoming interested in the study of sports analytics. 
keywords:
  - sports analytics
  - R packages
  - sports data
  - datasets
bibliography: [refs.bib, pkgs.bib]
biblio-style: unsrt   # use apa for WIRE
output: rticles::arxiv_article
---

>>>>

---
title: "Big Ideas in Sports Analytics and Statistical Tools for their Investigation"
authors:
  - name: Benjamin S. Baumer
    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
    department: Statistical & Data Sciences
    affiliation: Smith College
    location: Northampton, MA 01063
    email: bbaumer@smith.edu
    ORCID: 0000-0002-3279-0516
  - name: Gregory J. Matthews
    department: Mathematics and Statistics
    affiliation: Loyola University Chicago
    location: Chicago, IL 60660
    email: gmatthews1@luc.edu
    ORCID: 0000-0002-8413-5097
  - name: Quang Nguyen
    department: Mathematics and Statistics
    affiliation: Loyola University Chicago
    location: Chicago, IL 60660
    email: nnguyen22@luc.edu
abstract: |
  Sports analytics---broadly defined as the pursuit of improvement in athletic performance through the analysis of data---has expanded its footprint both in the professional sports industry and in academia over the past 30 years. We connect four(?) big ideas that are common across multiple sports, and explore both the shared similarities and individual idiosyncracies of analytical approaches in each sport. While our focus is on the concepts underlying each type of analysis, any implementation necessarily involves both statistical methodologies and sources of data. Where appropriate, we outline how data, models, and knowledge of the sport combine to generate actionable insights. This paper should serve as a useful overview for anyone becoming interested in the study of sports analytics. 
keywords:
  - sports analytics
  - R packages
  - sports data
  - datasets
bibliography: [refs.bib, pkgs.bib]
biblio-style: unsrt   # use apa for WIRE
output: rticles::arxiv_article
---
